Self-assembly of colloid-cholesteric composites: A route to switchable optical materials

### 2013-11-21 papers/2012-sandwich/CholColloids.tex
corrections
git-svn-id: https://ccpforge.cse.rl.ac.uk/svn/ludwig/trunk@2259 40876441-3496-0410-a613-a2fca35b2ae2

Fig.~2E-H shows comparable simulations for planar wall anchoring. 
Without colloids, planar anchoring results in a regular cholesteric helix,
with axis perpendicular to the boundary walls. 
This twisted texture develops via a set of defect loops,
which shrink and disappear to leave a defect-free sample. However,
dispersing particles with small $w$ arrests the loop shrinking process,
stabilising twisted rings (Fig.~2E) at small $\phi$, and more complicated 
double-stranded structures at larger $\phi$ (Fig.~2F).
For larger $w$, we observe thick colloidal ``ropes" about 5 colloids across
(Fig.~2E,H). These ropes undulate to follow the chiral structure of the 
underlying fluid. On increasing the density they develop branch points and finally again approach a percolating gel morphology. Note that planar wall anchoring is incompatible with the normal anchoring on the colloids (for $w>0$), which are thus repelled from both walls (see the side views in Fig.~2E-H).

@@

\centerline{\includegraphics[width=\textwidth]{text-fig1.jpg}}
\caption{Snapshots of the states obtained after dispersing
a suspension of colloidal nanoparticles within a cholesteric liquid
crystal in the BPI-forming region. (A-D) correspond to the case
of a dispersion of particles in a pre-equilibrated BPI phase;
(E-H) are obtained by dispersing colloids in an isotropic
phase and then quenching into the range where BPI is stable, leading to formation of an amorphous, BPIII-like, disclination network.
Structures correspond
to (A,E) $w=0.23$ and $\phi=1\%$, 
(B,F) $w=0.23$ and $\phi=5\%$, 
(C,G) $w=2.3$ and $\phi=1\%$,
(D,H) $w=2.3$ and $\phi=5\%$.
The anchoring of the director field to the colloidal surface is normal.
[For the full parameter list used to generate Figs.~1-3 see Supplementary
Information.] For clarity, only a portion of the simulation box (a quarter of
each axis in size) is shown; the full structures are shown in Supplementary
Fig. S2 and S3.}
\end{figure}

\begin{figure}
\centerline{\includegraphics[width=\textwidth]{text-fig2.jpg}}
\caption{Snapshots of the steady states obtained when a dispersion of colloids in the isotropic phase is placed in a sandwich geometry, 
and then quenched into a regime where BPI is stable in the bulk. Both top and side views are provided.
The anchoring of the director field at the walls is normal for (A-D) and planar for (E-H). 
Structures correspond to (A,E) $w=0.23$ and $\phi=1\%$, 
(B,F) $w=0.23$ and $\phi=2\%$, 
(C,G) $w=2.3$ and $\phi=1\%$,
(D,H) $w=2.3$ and $\phi=2\%$.
As in Fig. 1, only a portion of the simulation box is shown for clarity;
the full structures are shown in Supplementary Fig. S5 and S6.}
\end{figure}

>>>>

Fig.~2E-H shows comparable simulations for planar wall anchoring. 
Without colloids, planar anchoring results in a regular cholesteric helix,
with axis perpendicular to the boundary walls. 
This twisted texture develops via a set of defect loops,
which shrink and disappear to leave a defect-free sample. However,
dispersing particles with small $w$ arrests the loop shrinking process,
stabilising twisted rings (Fig.~2E) at small $\phi$, and more complicated 
double-stranded structures at larger $\phi$ (Fig.~2F).
For larger $w$, we observe thick colloidal ``ropes" about 5 colloids across
(Fig.~2G,H). These ropes undulate to follow the chiral structure of the 
underlying fluid. On increasing the density they develop branch points and finally again approach a percolating gel morphology. Note that planar wall anchoring is incompatible with the normal anchoring on the colloids (for $w>0$), which are thus repelled from both walls (see the side views in Fig.~2E-H).

@@

\centerline{\includegraphics[width=\textwidth]{text-fig1.jpg}}
\caption{Snapshots of the states obtained after dispersing
a suspension of colloidal nanoparticles within a cholesteric liquid
crystal in the BPI-forming region. (A-D) correspond to the case
of a dispersion of particles in a pre-equilibrated BPI phase;
(E-H) are obtained by dispersing colloids in an isotropic
phase and then quenching into the range where BPI is stable, leading to formation of an amorphous, BPIII-like, disclination network.
Structures correspond
to (A,E) $w=0.23$ and $\phi=1\%$;
(B,F) $w=0.23$ and $\phi=5\%$; 
(C,G) $w=2.3$ and $\phi=1\%$; and
(D,H) $w=2.3$ and $\phi=5\%$.
The anchoring of the director field to the colloidal surface is normal.
[For the full parameter list used to generate Figs.~1-3 see Supplementary
Information.] For clarity, only a portion of the simulation box is shown
(one eighth of the total volume); the full structures are shown in
Supplementary Fig. S2 and~S3.}
\end{figure}

\begin{figure}
\centerline{\includegraphics[width=\textwidth]{text-fig2.jpg}}
\caption{Snapshots of the steady states obtained when a dispersion of colloids in the isotropic phase is placed in a sandwich geometry, 
and then quenched into a regime where BPI is stable in the bulk. Both top and side views are provided.
The anchoring of the director field at the walls is normal for (A-D) and planar for (E-H). 
Structures correspond to (A,E) $w=0.23$ and $\phi=1\%$, 
(B,F) $w=0.23$ and $\phi=2\%$, 
(C,G) $w=2.3$ and $\phi=1\%$,
(D,H) $w=2.3$ and $\phi=2\%$.
As in Fig. 1, only one quarter of the simulation box is shown for clarity;
the full structures are shown in Supplementary Fig. S5 and S6.}
\end{figure}

### 2013-11-21 papers/2012-sandwich/support.tex
Updated pictures Nat Mater draft
git-svn-id: https://ccpforge.cse.rl.ac.uk/svn/ludwig/trunk@2244 40876441-3496-0410-a613-a2fca35b2ae2
corrections
git-svn-id: https://ccpforge.cse.rl.ac.uk/svn/ludwig/trunk@2259 40876441-3496-0410-a613-a2fca35b2ae2

{\bf Supplementary Information for: Self-assembly of colloid-cholesteric
composites: A route to switchable optical materials}

@@

The thermodynamics of the cholesteric liquid crystal can be described
by means of a  Landau-de Gennes free energy functional $\cal F$,
whose density is written as $f$:
\begin{eqnarray}
{\cal F}[{\bf Q}]&=&\int d^3{\bf r} f({\bf Q}({\bf r})).
\end{eqnarray}
This free energy density $f = f({\bf Q})$ may be expanded in powers of the
order parameter ${\bf Q}$ and its gradients; ${\bf Q}$ is a traceless 
and symmetric tensor which we will denote from now on in subscript
notation as $Q_{\alpha\beta}$.
The largest eigenvalue $q$ and corresponding eigenvector $n_\alpha$
of $Q_{\alpha\beta}$ describe the local strength and major orientation axis
of molecular order.
The theory based on the tensor $Q_{\alpha\beta}$, rather than a theory based
solely
on the director field $n_\alpha ({\bf r})$, allows treatment of disclinations
(defect lines) in whose cores $n_\alpha$ is undefined.

@@

To generate a disordered network of disclination lines, a ``quench''
is performed in which the order parameter is initialised via a
locally chosen random director, and
Eq.~\ref{eq:surf_q} employed with a small amplitude $q^0 = 10^{-7}$ to
provide an order parameter.
We avoid the mean-field spinodal point at $\gamma = 3.0$:
the parameters are the same as for the initial simulations with
pitch $p = 32\sqrt{2}$. The chirality and reduced temperature (see
Table~\ref{table:params}) remain appropriate for BPI.
Colloids are added as before and the simulations run for 2 million
simulation steps.

For simplicity, we do not allow the size of the BPI unit cell to 
dynamically readjust to minimize free energy (there is no 
``redshift''~\cite{blue1}): this would lead to quantitatively different 
values of the free energy, but qualitatively similar structures.

@@

In order to demonstrate structural information about the field-aligned 
states and the residual anisotropy after switch off we followed a 
procedure similar to the one described in \cite{oliver-bp3}.
The structure factor in the current approach is defined via
the Fourier transform of the colloid density:

\begin{eqnarray}
S({\bf k})&=&|F({\bf k})|^2\\
F({\bf k})&=&\int_V d{\bf r} \rho({\bf r}) e^{i {\bf k r}}
\end{eqnarray}

The colloid density $\rho({\bf r})$ is a discretised density and taken to be
$\rho({\bf r})=1$ if a lattice site at ${\bf r}$ is part of a colloid
and $\rho({\bf r})=0$ otherwise. This definition, which deviates from the 
standard definition of a structure factor and does not consider the colloids 
as pointlike objects, allows to gain the same structural information
in a simpler way.

@@

\bibitem{blue1}
D.C. Wright and N.D. Mermin,
%  Crystalline liquids -- the blue phases.
{\it Rev. Mod. Phys.} {\bf 61,} 385-432 (1989).
\bibitem{deGennes}
P.-G. de Gennes, J. Prost,
{\it The Physics of Liquid Crystals} (Oxford Univ. Press, New York, 1993).
%\bibitem{marendu1}
%D. Marenduzzo, E.  Orlandini, M. E. Cates, J. M. Yeomans,
%{\rm Steady-state hydrodynamic instabilities of active liquid crystals:
%Hybrid lattice Boltzmann simulations.}
%{\it Phys. Rev. E} {\bf 76}, 031921 (2007).
%\bibitem{marendu2}
%O. Henrich, D. Marenduzzo, K. Stratford, M. E. Cates, 
%{\rm Domain growth in cholesteric blue phases:
%hybrid lattice Boltzmann simulations}.
%{\it Comput. Math. Appl.}, doi:10.1016/j.camwa.2009.08.047[dx.doi.org] (2009).
%\bibitem{marendu3}
%M. E. Cates, O. Henrich, D. Marenduzzo, K. Stratford,
%{\rm  Lattice Boltzmann simulations of liquid crystalline fluids:
%active gels and blue phases.}
%{\it Soft Matter} {\bf 5}, 3791-3800 (2009).
\bibitem{oliver1}
O. Henrich, D. Marenduzzo, K. Stratford, and M.E. Cates,
%Thermodynamics of blue phases in electric fields
\textit{Phys. Rev. E}, \textbf{81} 031706 (2010).
\bibitem{beris}
A. N. Beris, B. J. Edwards, 
{\it Thermodynamics of Flowing Systems with Internal Microstructure}
(Oxford Univ. Press, New York, 1994).
\bibitem{ladd94}
A.J.C. Ladd,
\textit{J. Fluid Mech.} \textbf{271}, 285 (1994); \textit{ibid.} \textbf{271}
311 (1994).
\bibitem{nguyen2002}
N.-Q. Nguyen and A.J.C. Ladd,
\textit{Phys. Rev. E} \textbf{66} 046708 (2002).
\bibitem{juho}
J.S. Lintuvuori, D. Marenduzzo, K. Stratford, and M.E. Cates,
\textit{J. Mater. Chem.} \textbf{20}, 10547 (2010).
\bibitem{denniston}
C. Denniston, E. Orlandini, J. M. Yeomans, 
\textit{Phys. Rev. E} \textbf{63}, 056702 (2001).
\bibitem{fournier2005}
J.-B. Fournier and P. Galatola,
\textit{Europhys. Lett.} \textbf{72}, 403 (2005).
\bibitem{oliver-bp3}
O. Henrich, K. Stratford, M.~E. Cates, D. Marenduzzo,
{\it Phys. Rev. Lett.} {\bf 106}, 107802 (2011).
\bibitem{denniston2}
C. Denniston, D. Marenduzzo, E. Orlandini, J. M.  Yeomans, 
\textit{Philos. Trans. R. Soc. London, Ser. A} \textbf{362}, 1745 (2004).
\bibitem{oliver2}
O. Henrich, K. Stratford, D. Marenduzzo, M. E. Cates, 
\textit{Proc. Acad. Sci. USA} \textbf{107}, 1312 (2010).
\bibitem{codef} M. E. Cates,  et al., 
\textit{J. Phys. Condens. Matter} \textbf{16},  3903 (2004).

@@

{\bf Supplementry Figures and Animations}

@@

\begin{figure}[!h]
\begin{center}
\includegraphics[width=0.32\columnwidth]{col_parallel_x_run1341.png}
\includegraphics[width=0.32\columnwidth]{sq_x_run1341.png}
\includegraphics[width=0.32\columnwidth]{sq_y_run1341.png}
\includegraphics[width=0.32\columnwidth]{col_parallel_x_run1342.png}
\includegraphics[width=0.32\columnwidth]{sq_x_run1342.png}
\includegraphics[width=0.32\columnwidth]{sq_y_run1342.png}
\end{center}
\caption{Structure with and without electric field, with disclination lines
removed for clarity. Panels A and B reproduce the results in Fig. 3C and
Fig. 3D respectively with the applied field in the $x$-direction 
(out of the plane of the paper). Also included is a cut of the structure 
factor with $k_y = 0$ (panel C). 
Panels D, E, and F show the corresponding situation after the
external field has been removed and the structure allowed to relax,
and show residual hexagonal ordering. The structure factor data is for wave
vectors $k_x = 0; (k_y, k_z) \in [-3\pi/8 , 3\pi/8]$ (panels B and E) and
$k_y = 0; (k_x, k_z) \in [-3\pi/8, 3\pi/8]$ (panels C and F).}
\end{figure}

@@

\begin{figure}[!h]
\begin{center}
\includegraphics[width=0.32\columnwidth]{col_parallel_y_run1343.png}
\includegraphics[width=0.32\columnwidth]{sq_x_run1343.png}
\includegraphics[width=0.32\columnwidth]{sq_y_run1343.png}\\
\includegraphics[width=0.32\columnwidth]{col_parallel_y_run1344.png}
\includegraphics[width=0.32\columnwidth]{sq_x_run1344.png}
\includegraphics[width=0.32\columnwidth]{sq_y_run1344.png}\\
\end{center}
\caption{Cycling the electric field. Starting from the final position of
Supplementary Fig.~7 panel~D, the field is re-applied, this time in the
$y$-direction. The corresponding view of the particle distribution is
shown, again viewing along the field direction, in panel A.
Corresponding structure factor cuts with $k_x = 0$ and $k_y = 0$ are
shown in panels B and C, respectively. The corresponding situation when
the field is again switched off, and the structure allowed to relax,
is shown in panels d, E, and F. The wave vector values used are the
same as in Supplementary Fig.~7.}
\end{figure}

@@

\begin{figure}[!h]
\begin{center}
\includegraphics[width=0.32\columnwidth]{col_parallel_x_run1345.png}
\includegraphics[width=0.32\columnwidth]{sq_x_run1345.png}
\includegraphics[width=0.32\columnwidth]{sq_y_run1345.png}\\
\includegraphics[width=0.32\columnwidth]{col_parallel_x_run1347.png}
\includegraphics[width=0.32\columnwidth]{sq_x_run1347.png}
\includegraphics[width=0.32\columnwidth]{sq_y_run1347.png}
\end{center}
\caption{Cycling the electric field further. Starting from the final
position of Supplementary Fig.~8 panel~D, the field is re-applied
again in the $x-$direction. Panel A shows the particle configuration
viewed along the field direction, and panels B and C show the structure
factor with $k_x = 0$ and $k_y = 0$ respectively. The corresponding
situation when the field is removed and the structure allowed to relax
is shown in panels D, E, and F. The wave vector values are again as
in Supplementary Fig.~7. Note that the on and off states are 
equivalent to those in Supplementary Fig.~7, up to a rotation.
This is because all hexagonal structures perpendicular to the field
direction are energetically degenerate,
and the actual orientation of the hexagon emerges spontaneously during
switching. }
\end{figure}

>>>>

{\bf
Self-assembly of colloid-cholesteric
composites: A route to switchable optical materials.

Supplementary Information}

@@

The thermodynamics of the cholesteric liquid crystal can be described
by means of a  Landau-de Gennes free energy functional $\cal F$,
whose density is written as $f$:
\begin{eqnarray}
{\cal F}[{\bf Q}]&=&\int d^3{\bf r} f({\bf Q}({\bf r})).
\end{eqnarray}
This free energy density $f = f({\bf Q})$ may be expanded in powers of the
order parameter ${\bf Q}$ and its gradients; ${\bf Q}$ is a traceless 
and symmetric tensor which is denoted from now on in subscript
notation as $Q_{\alpha\beta}$.
The largest eigenvalue $q$ and corresponding eigenvector $n_\alpha$
of $Q_{\alpha\beta}$ describe the local strength and major orientation axis
of molecular order.
The theory based on the tensor $Q_{\alpha\beta}$, rather than a theory based
solely
on the director field $n_\alpha ({\bf r})$, allows treatment of disclinations
(defect lines) in whose cores $n_\alpha$ is undefined.

@@

To generate a disordered network of disclination lines, a ``quench''
is performed in which the order parameter is initialised via a
locally chosen random director, and
Eq.~\ref{eq:surf_q} employed with a small amplitude $q^0 = 10^{-7}$ to
provide an order parameter.
The mean-field spinodal point at $\gamma = 3.0$ is avoided and
the parameters are the same as for the initial simulations with
pitch $p = 32\sqrt{2}$. The chirality and reduced temperature (see
Table~\ref{table:params}) remain appropriate for BPI.
Colloids are added as before and the simulations run for 2 million
simulation steps.

For simplicity,  the size of the BPI unit cell is not allowed to 
readjust dynamically to minimize free energy (there is no 
``redshift''~\cite{blue1}): this would lead to quantitatively different 
values of the free energy, but qualitatively similar structures.

@@

To provide structural information about the field-aligned 
states and the residual anisotropy after switch off a 
procedure similar to the one described in \cite{oliver-bp3} is
followed.
The structure factor $S(\mathbf{k})$ in the current approach is
defined via the Fourier transform of the colloid density $F(\mathbf{k})$:

%\begin{eqnarray}
%S({\bf k})&=&|F({\bf k})|^2,\\
%F({\bf k})&=&\int d^3{\bf r} \rho({\bf r}) e^{i {\bf k. r}}.
%\end{eqnarray}

\begin{equation}
S({\bf k}) =  |F({\bf k})|^2, \mathrm{with}\
F({\bf k}) = \int d^3{\bf r} \rho({\bf r}) e^{i {\bf k. r}}.
\end{equation}

The colloid density $\rho({\bf r})$ is a discretised density and taken to be
$\rho({\bf r})=1$ if a lattice site at ${\bf r}$ is part of a colloid
and $\rho({\bf r})=0$ otherwise. This definition, which deviates from the 
standard definition of a structure factor and does not consider the colloids 
as point-like objects, allows the same structural information
to be obtained in a simple way.

@@

\bibitem{blue1}
D.C. Wright and N.D. Morin,
%  Crystalline liquids -- the blue phases.
{\it Rev. Mod. Phys.} {\bf 61,} 385-432 (1989).
\bibitem{deGennes}
P.-G. DEC Gunner's, J. Poorest,
{\it The Physics of Liquid Crystals} (Oxford Univ. Press, New York, 1993).
%\bibitem{marendu1}
%D. Marenduzzo, E.  Orlandini, M. E. Cates, J. M. Yeomans,
%{\rm Steady-state hydrodynamic instabilities of active liquid crystals:
%Hybrid lattice Boltzmann simulations.}
%{\it Phys. Rev. E} {\bf 76}, 031921 (2007).
%\bibitem{marendu2}
%O. Henrich, D. Marenduzzo, K. Stratford, M. E. Cates, 
%{\rm Domain growth in cholesteric blue phases:
%hybrid lattice Boltzmann simulations}.
%{\it Comput. Math. Appl.}, doi:10.1016/j.camwa.2009.08.047[dx.doi.org] (2009).
%\bibitem{marendu3}
%M. E. Cates, O. Henrich, D. Marenduzzo, K. Stratford,
%{\rm  Lattice Boltzmann simulations of liquid crystalline fluids:
%active gels and blue phases.}
%{\it Soft Matter} {\bf 5}, 3791-3800 (2009).
\bibitem{oliver1}
O. Henrich, D. Marenduzzo, K. Stratford, and M.E. Cates,
%Thermodynamics of blue phases in electric fields
\textit{Phys. Rev. E}, \textbf{81} 031706 (2010).
\bibitem{beris}
A. N. Beris, B. J. Edwards, 
{\it Thermodynamics of Flowing Systems with Internal Microstructure}
(Oxford Univ. Press, New York, 1994).
\bibitem{ladd94}
A.J.C. Ladd,
\textit{J. Fluid Mech.} \textbf{271}, 285 (1994); \textit{ibid.} \textbf{271}
311 (1994).
\bibitem{nguyen2002}
N.-Q. Nguyen and A.J.C. Ladd,
\textit{Phys. Rev. E} \textbf{66} 046708 (2002).
\bibitem{juho}
J.S. Lintuvuori, D. Marenduzzo, K. Stratford, and M.E. Cates,
\textit{J. Mater. Chem.} \textbf{20}, 10547 (2010).
\bibitem{denniston}
C. Denniston, E. Orlandini, J. M. Yeomans, 
\textit{Phys. Rev. E} \textbf{63}, 056702 (2001).
\bibitem{fournier2005}
J.-B. Fournier and P. Galatola,
\textit{Europhys. Lett.} \textbf{72}, 403 (2005).
\bibitem{oliver-bp3}
O. Henrich, K. Stratford, M.~E. Cates, D. Marenduzzo,
{\it Phys. Rev. Lett.} {\bf 106}, 107802 (2011).
\bibitem{denniston2}
C. Denniston, D. Marenduzzo, E. Orlandini, J. M.  Yeomans, 
\textit{Philos. Trans. R. Soc. London, Ser. A} \textbf{362}, 1745 (2004).
\bibitem{oliver2}
O. Henrich, K. Stratford, D. Marenduzzo, M. E. Cates, 
\textit{Proc. Acad. Sci. USA} \textbf{107}, 1312 (2010).
\bibitem{codef} M. E. Cates,  et al., 
\textit{J. Phys. Condens. Matter} \textbf{16},  3903 (2004).

@@

{\bf Supplementary Figures and Animations}

@@

\begin{figure}[!h]
\begin{center}
\includegraphics[width=0.34\columnwidth]{col_parallel_x_run1341.png}
\includegraphics[width=0.32\columnwidth]{sq_x_run1341_2.png}
\includegraphics[width=0.32\columnwidth]{sq_y_run1341.png}
\includegraphics[width=0.34\columnwidth]{col_parallel_x_run1342.png}
\includegraphics[width=0.32\columnwidth]{sq_x_run1342.png}
\includegraphics[width=0.32\columnwidth]{sq_y_run1342.png}
\end{center}
\caption{Structure with and without electric field, with disclination lines
removed for clarity. Panels A and B reproduce the results in Fig. 3C and
Fig. 3D respectively with the applied field in the $x$-direction 
(out of the plane of the paper). Also included is a cut of the structure 
factor with $k_y = 0$ (panel C). 
Panels D, E, and F show the corresponding situation after the
external field has been removed and the structure allowed to relax,
and show residual hexagonal ordering. The structure factor data is for wave
vectors $k_x = 0; (k_y, k_z) \in [-3\pi/8 , 3\pi/8]$ (panels B and E) and
$k_y = 0; (k_x, k_z) \in [-3\pi/8, 3\pi/8]$ (panels C and F).}
\end{figure}

@@

\begin{figure}[!h]
\begin{center}
\includegraphics[width=0.34\columnwidth]{col_parallel_y_run1343.png}
\includegraphics[width=0.32\columnwidth]{sq_x_run1343.png}
\includegraphics[width=0.32\columnwidth]{sq_y_run1343.png}\\
\includegraphics[width=0.34\columnwidth]{col_parallel_y_run1344.png}
\includegraphics[width=0.32\columnwidth]{sq_x_run1344.png}
\includegraphics[width=0.32\columnwidth]{sq_y_run1344.png}\\
\end{center}
\caption{Cycling the electric field. Starting from the final position of
Supplementary Fig.~7 panel~D, the field is re-applied, this time in the
$y$-direction. The corresponding view of the particle distribution is
shown, again viewing along the field direction, in panel A.
Corresponding structure factor cuts with $k_x = 0$ and $k_y = 0$ are
shown in panels B and C, respectively. The corresponding situation when
the field is again switched off, and the structure allowed to relax,
is shown in panels d, E, and F. The wave vector values used are the
same as in Supplementary Fig.~7.}
\end{figure}

@@

\begin{figure}[!h]
\begin{center}
\includegraphics[width=0.34\columnwidth]{col_parallel_x_run1345.png}
\includegraphics[width=0.32\columnwidth]{sq_x_run1345.png}
\includegraphics[width=0.32\columnwidth]{sq_y_run1345.png}\\
\includegraphics[width=0.34\columnwidth]{col_parallel_x_run1347.png}
\includegraphics[width=0.32\columnwidth]{sq_x_run1347.png}
\includegraphics[width=0.32\columnwidth]{sq_y_run1347.png}
\end{center}
\caption{Cycling the electric field further. Starting from the final
position of Supplementary Fig.~8 panel~D, the field is re-applied
again in the $x-$direction. Panel A shows the particle configuration
viewed along the field direction, and panels B and C show the structure
factor with $k_x = 0$ and $k_y = 0$ respectively. The corresponding
situation when the field is removed and the structure allowed to relax
is shown in panels D, E, and F. The wave vector values are again as
in Supplementary Fig.~7. Note that the on and off states are 
equivalent to those in Supplementary Fig.~7, up to a rotation.
This is because all hexagonal structures perpendicular to the field
direction are energetically degenerate,
and the actual orientation of the hexagon emerges spontaneously during
switching. }
\end{figure}
